\documentclass{article}
\usepackage[a4paper, left=2cm, right=2cm, top=2cm, bottom=2cm,textwidth=17cm,textheight=23cm]{geometry}
\usepackage{xeCJK}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tikz}
\setCJKmainfont{標楷體-繁}
\setmainfont{Times New Roman}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\fancyhead[L]{Enrollment document}
\fancyhead[R]{9 Jun. 2025}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\title{Enrollment document}
\author{Tom T. Hsiao}
\date{9 Jun. 2025}
\begin{document}
\setstretch{1.5}
\thispagestyle{fancy}
\begin{center}
\fontsize{16pt}{16pt}\selectfont Enrollment document
\end{center}
\fontsize{14pt}{14pt}\selectfont
This document explains some requirements for those who want to enroll in this course, there are \textcolor{red}{5} requirements available, the limited space in our classroom is \textcolor{red}{65} seats. \\
The priority of enrollment is based on the following orders: \\
I. P.T. > I.R. and P.A. > S.S. major > Other major. \\
II. Freshman > Senior or above > Junior > Sophomore. 
\begin{enumerate}
\item Some of the requirements are:
\begin{enumerate}
\item You can write in English or Mandarin.
\item Your file must be named as ID.pdf.
\end{enumerate}
\item The file must have:
\begin{enumerate}
\item Font: Times New Roman for English or numeric and BiauKai for Mandarin.
\item Font size at least 13pt in content and 15pt in title.
\item Header and Footer.
\item Title, author with department, ID, name, and date.
\item \textcolor{red}{A space} between mandarin and english or numeric.
\item Suitable line spacing, at least 1.5.
\item Your motivation at most \textcolor{red}{a hundred} words.
\end{enumerate}
\item Some bonus points:
\begin{enumerate}
\item LaTeX edit can earn an extra points, see properties of your pdf file.
\item English writing with less grammar mistakes or syntax errors can earn an extra point.
\end{enumerate}
\item After you finish your document, please send it to my email with subject line as following format:
\begin{verbatim}
[Politics] #ID - Enroll letter
\end{verbatim}
\item The period counts on \textcolor{red}{08:00 to 18:00 (NST), Wednesday to Friday (Week 01)}, earlier or later must be rejected, the result will be published on the course webpage before week 02.
\end{enumerate}
\end{document}
