\documentclass{article}
\usepackage[a4paper, left=2cm, right=2cm, top=2cm, bottom=2cm,textwidth=17cm,textheight=23cm]{geometry}
\usepackage{xeCJK}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\setCJKmainfont{標楷體-繁}
\setmainfont{Times New Roman}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\textsf{\thepage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\title{\fontsize{16pt}{16pt}\selectfont Politics}
\author{}
\date{}
\begin{document}
\setstretch{1.05}
\maketitle
\fontsize{14pt}{14pt}\selectfont
Instructor Information \\
\begin{itemize}
\item Instructor: Dr. Tzu-Chi Hsiao. \\
\item Office: Room 703, Department of Political Science. \\
\item Office hours: 08:10-09:00, Every Tuesday. \\
\item Email: \href{mailto:politics.tchsiao@gmail.com}{politics.tchsiao@gmail.com}. \\
\item Webpage: \href{https://politics-tchsiao.github.io/website/}{https://politics-tchsiao.github.io/website/}. \\
\end{itemize}
Course Information \\
\begin{itemize}
\item Course: Politics. \\
\item Credit: 3. \\
\item Hours: 09:10-12:00, Every Tuesday. \\
\item Prerequisite: High school civics. \\
\item Webpage: \href{https://politics-tchsiao.github.io/politics/}{https://politics-tchsiao.github.io/politics/}. \\
\item Course description \\
In this course, we must study a series of knowledge based on your high school's civics, and extend to subset of Political Science. \\ 
\item Course objectives \\
1. To understand the basic concepts of political science. \\
2. To understand the basic concepts of political philosophy. \\
3. To understand the basic concepts of public administration. \\
\end{itemize}
\newpage
Grading \\
\begin{itemize}
\item Midterm exam: 50\%. \\
\item Final exam: 50\%. \\
\end{itemize}
Textbook \\
\begin{itemize}
\item \textit{Politics}, latest edition, written by Dr. Andew Heywood. \\
\end{itemize}
Course Schedule \\
\begin{itemize}
\item Please refer to the \href{https://politics-tchsiao.github.io/politics/}{course webpage}. \\
\end{itemize}
Average Equality Policy \\
\begin{itemize}
\item The average of the course is between 75.5 to 76.4, based on your performance in attendance. \\
\item The highest score is not exceed 99, if you got a hundred in your midterm \textcolor{red}{or} final examination. \\
\item I may given whom score is between 57.5 to 59.4 to C\textsuperscript{-}.
\end{itemize}
\end{document}